Generating Simulated Data

### 2021-03-15 docs/SimData.Rmd
foodweb and speciesList files for hydra

ms_diet <- diettrue %>%
  filter(species %in% sppsubset$Name) %>%
  filter(atoutput>0)

predOrPrey <- ms_diet %>%
  filter(prey %in% unique(species)) %>%
  select(species, agecl, time.days, prey, atoutput) %>%
  group_by(species, prey) %>%
  summarise(avgpreyprop = mean(atoutput))

specieslist <- data.frame(species = unique(unique(survObsBiom[[2]][[1]]$species)),
                          guild = rep("na"),
                          guildmember = c(1:11),
                          predOrPrey = rep(1)
)

>>>>

ms_diet <- diettrue %>%
  filter(species %in% sppsubset$Name) %>%
  filter(atoutput>0) %>%
  mutate(species = as.character(species),
         prey = as.character(prey))

predPrey <- ms_diet %>%
  filter(prey %in% unique(species)) %>%
  select(species, agecl, time.days, prey, atoutput) %>%
  group_by(species, prey) %>%
  summarise(avgpreyprop = mean(atoutput))

foodweb <- left_join(sppsubset, predPrey, by=c("Name" = "species")) %>%
  select(species, prey, avgpreyprop) %>%
  mutate(avgpreyprop = ceiling(avgpreyprop)) %>%
  spread(species, avgpreyprop) %>%
  filter(!is.na(prey)) %>%
  replace(is.na(.), 0)

predOrPrey <- ifelse(colSums(foodweb[-1])>0, 1, 0)

specieslist <- data.frame(species = unique(unique(survObsBiom[[2]][[1]]$species)),
                          guild = rep("na"),
                          guildmember = c(1:11),
                          predOrPrey = predOrPrey
)

o.name <- here("simulated-data/msinput/hydra/")
write_csv(foodweb, paste0(o.name,"foodweb_NOBA.csv"))
write_csv(specieslist, paste0(o.name,"speciesList_NOBA.csv"))
